Summary Tables

### 2022-01-19 summary_tables.Rmd
Save both as CSV and excel sheet - health outcomes. Ref #86

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
library(data.table)
})

@@

>>>>

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
library(data.table)
library(writexl)
})

@@

# # Export deaths HB
# path_deaths_wb <- "results/multi_city/health_impacts/Deaths.xlsx"
# deaths_wb <- readWorkbook(path_deaths_wb)
# wb <-  loadWorkbook(path_deaths_wb)
# removeTable(wb = wb, sheet = "Deaths", table = "Tabla1")
# writeDataTable(wb, sheet = "Deaths", x = rbindlist(health$deaths$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "Deaths_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "Deaths_Pathway", x = rbindlist(health$deaths$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_deaths_wb, overwrite =TRUE)
# 
# # Export ylls HB
# path_ylls_wb <- "results/multi_city/health_impacts/YLLs.xlsx"
# ylls_wb <- readWorkbook(path_ylls_wb)
# wb <-  loadWorkbook(path_ylls_wb)
# removeTable(wb = wb, sheet = "YLLs", table = "Tabla1")
# writeDataTable(wb, sheet = "YLLs", x = rbindlist(health$ylls$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "YLLs_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "YLLs_Pathway", x = rbindlist(health$ylls$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_ylls_wb, overwrite =TRUE)

# # Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls_hb_lng = rbindlist(health$ylls$hb, use.names = T),
                         ylls_pathway_hb_lng = rbindlist(health$ylls$pathway_hb, use.names = T),
                         Deaths = rbindlist(health$deaths$hb, use.names = T),
                         Deaths_Pathway = rbindlist(health$deaths$pathway_hb, use.names = T)), path = output_file)
